### 2023-06-14 resilience.tex
up

\problemx{resilience problem (RP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $\Safe, \Bad \subseteq S$.}
{$\Bad \longrightarrow^{*} \Safe$ ?\newline}
%
%\alain{il faudrait ne pas répéter 3 fois les mêmes imputs pour les 3 pbs: énoncer les 3 uniformes pbs d'un coup avec une fois l'input puis les 3 pbs pour un état s donné sans répéter non plus 3 fois les mêmes inputs}

%We add a third problem that decides whether there exists an $k$ such  that the system is $k$-resilient.
%

@@

@@

% \begin{remark}[Reformulation]\label{reformulation}
% $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
% (\Safe, \Bad)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
% $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
% (\Safe, \Bad)-$k$-resilient iff $\Bad \subseteq \pred^{\leq k}(\Safe)$.
% \end{remark}

These three resilience problems are decidable for finite transition systems but undecidable for (general) infinite-state transition systems. So we restrict our framework to the class of infinite-state WSTS. Since most of decidable properties in WSTS rely on the computation of upward or downward-closed sets \cite{DBLP:journals/iandc/AbdullaCJT00, DBLP:journals/tcs/FinkelS01}, we consider upward-closed or downward-closed sets $\Safe$ and $\Bad$. In \cite{DBLP:journals/corr/abs-2108-00889}, the authors considered that $\Bad$ is downward-closed and $\Safe$ is upward-closed.

Surprinsingly, we have not found decidability results about the resilience problems for WSTS.
%		
We deduce 
% \textcolor{red}{that the three resilience problems are decidable for all four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed sets.}
% \mathieu{changer ça}
decidability results for the four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed as seen in Section~\ref{synthesis}.
In particular, the existing proofs of resilience use the decidability of reachability; but we wish to decide resilience for models with undecidable reachability.
%
%	 and ideals are recursive 
Our result will rely on coverability instead of reachability. We moreover show undecidability when coverability is not decidable in the case $\Safe = \uparrow \Safe$.

@@

>>>>

\iffalse
\problemx{resilience problem (RP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $\Safe, \Bad \subseteq S$.}
{$\Bad \longrightarrow^{*} \Safe$ ?\newline}

\alain{il faudrait ne pas répéter 3 fois les mêmes imputs pour les 3 pbs: énoncer les 3 uniformes pbs d'un coup avec une fois l'input puis les 3 pbs pour un état s donné sans répéter non plus 3 fois les mêmes inputs}

@@

\fi

\problemx{resilience problems}
{A transition system $\mathscr{S}=(S,\rightarrow)$, two sets $\Safe, \Bad \subseteq S$, $k \in \mathbb{N}$.}
{ ({\sc resilience problem (RP)}) $\Bad \longrightarrow^{*} \Safe$ ?\newline  
({\sc $k$-resilience problem (kRP)})		$\Bad \longrightarrow^{\leq k} \Safe$ ?\newline
({\sc $k$-resilience problem (kRP)})	$\exists k \geq 0$ such that $\mathscr{S}$ is 
 $k$-resilient ?\newline}

@@

These three resilience problems are decidable for finite transition systems but undecidable for (general) infinite-state transition systems. So we restrict our framework to the class of infinite-state WSTS. Since most of decidable properties in WSTS rely on the computation of upward or downward-closed sets \cite{DBLP:journals/iandc/AbdullaCJT00, DBLP:journals/tcs/FinkelS01}, we consider upward-closed or downward-closed sets $\Safe$ and $\Bad$. In \cite{DBLP:journals/corr/abs-2108-00889}, the authors considered that $\Bad$ is downward-closed and $\Safe$ is upward-closed. \mathieu{Remarquer que dans l'example~\ref{Example} on a à la fois upward closed ET downward closed pour $\Safe$ ET $\Bad$.}

Surprinsingly, we have not found decidability results about the resilience problems for WSTS.	
We deduce decidability results for the four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed as seen in Section~\ref{synthesis}.
In particular, the existing proofs of resilience use the decidability of reachability; but we wish to decide resilience for models with undecidable reachability.
%
%	 and ideals are recursive 
Our result will rely on coverability instead of reachability. We moreover show undecidability when coverability is not decidable in the case $\Safe = \uparrow \Safe$
and in the general case when $\Safe = \downarrow \Safe$.

@@

\mathieu{Beaucoup plus dévellopper le paragraphe ci-dessus et expliciter qu'à partir de maintenant, on considère $\Bad$ complémentaire de $\Safe$ par défaut.}
